Supporting Information:\n prolfqua - A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2022-10-25 inst/MyArticle/prolfqua_supplement.Rmd
Fix typo

In the code snippet below, we we test if we should reject the null hypothesis that the area under the ROC curve at 0.1 FDR does not differ for  msqrob2, proDA, and prolfqua when computed based on scaled p.values. To this task we use the function roc.test from the R package `r BiocStyle::CRANpkg("pROC")`.

>>>>

In the code snippet below, we test if we should reject the null hypothesis that the area under the ROC curve at 0.1 FDR does not differ for  msqrob2, proDA, and prolfqua when computed based on scaled p.values. To this task we use the function roc.test from the R package `r BiocStyle::CRANpkg("pROC")`.
